Non-word repetition in Yélî Dnye

### 2021-09-02 manuscript.Rmd
bug found but not fixed: looking into widone 12

#read.table("substitution_bank_try1.txt",header=T)->sub_bank
read.table("substitution_bank.txt",header=T)->sub_bank_full
colnames(sub_bank_full)<-c("target","realization","age")
sub_bank=sub_bank_full[,1:2]
sub_bank$target=factor(sub_bank$target,levels=allVC)
sub_bank$realization=factor(sub_bank$realization,levels=allVC)

@@

#read.table("deletion_bank_try1.txt",header=T)->del_bank
read.table("deletion_bank.txt",header=T)->del_bank_full
colnames(del_bank_full)<-c("target","age")
del_bank=del_bank_full[,1]
del_bank$target=factor(del_bank$target,levels=allVC)
del_tab= table(del_bank)[allVC]

#read.table("match_bank_try1.txt",header=T)->match_bank
read.table("match_bank.txt",header=T)->match_bank_full
colnames(match_bank_full)<-c("target","age")
match_bank=match_bank_full[,1]
match_bank$target=factor(match_bank$target,levels=allVC)
match_tab= table(match_bank)[allVC]

>>>>

#read.table("substitution_bank_try1.txt",header=T)->sub_bank
read.table("substitution_bank.txt",header=T)->sub_bank_full
colnames(sub_bank_full)<-c("target","realization","age","target_ortho","phono","tokid")
sub_bank=sub_bank_full[,1:2]
sub_bank$target=factor(sub_bank$target,levels=allVC)
sub_bank$realization=factor(sub_bank$realization,levels=allVC)

@@

#read.table("deletion_bank_try1.txt",header=T)->del_bank
read.table("deletion_bank.txt",header=T)->del_bank_full
colnames(del_bank_full)<-c("target","age","target_ortho","phono","tokid")
del_bank=del_bank_full[,1]
del_bank$target=factor(del_bank$target,levels=allVC)
del_tab= table(del_bank)[allVC]

#read.table("match_bank_try1.txt",header=T)->match_bank
read.table("match_bank.txt",header=T)->match_bank_full
colnames(match_bank_full)<-c("target","age","target_ortho","phono","tokid")
match_bank=match_bank_full[,1]
match_bank$target=factor(match_bank$target,levels=allVC)
match_tab= table(match_bank)[allVC]
